IRTF Spectro-Photometry of Two Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-11-20 ms.tex
I touched up some of the intro and description of the time series.

We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a period of 3 hr.
The basic properties of each system are listed in Table \ref{tab:bdProp}.

@@

Figure \ref{fig:specphot} shows the dynamic spectra for both brown dwarfs with the individual spectra of the target and reference stars on the upper panels.
At the $\lesssim 1$\% level, 2MASS J0835 shows no variations or systematics.
2MASS J1821 on the other hand, shows a periodic signal that is strongest at the short wavelength and gradually gets smaller toward longer wavelengths.
2MASS J1821 also exhibits systematic trends near strong slopes in the raw spectra due to telluric absorption bands.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system. Alternating colors are used to distinguished the light curves with offsets.}
	\label{fig:tserPfold}
\end{figure*}

2MASS J0835 exhibits no periodic behavior whereas 2MASS 1821 shows large varations when phasing the dynamic spectra at the known rotation periods of the two brown dwarfs, shown in Figure \ref{fig:tserPfold}.
For 2MASS 1821, the variations are mostly sinusoidal and repeat over multiple rotations of the brown dwarf - the exception is wavelengths near telluric features, such as 1.43~$\mu$m and 1.79~$\mu$m.

>>>>

We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres with the techniques of \citet{schlawin2014} to achieve high precision spectro-photometry.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a tentative period of 3 hr \citep{koen2004ibandBD}, which also permitted multiple rotation periods.
The basic properties of each system are listed in Table \ref{tab:bdProp}.

@@

Figure \ref{fig:specphot} shows the dynamic spectra for both brown dwarfs with the individual spectra of the target and reference stars on the upper panels.
At the $\lesssim 1$\% level, 2MASS J0835 shows no variations or systematics.
2MASS J1821 on the other hand, shows a periodic signal that is strongest at the short wavelength and gradually gets smaller toward longer wavelengths.
2MASS J1821 also exhibits systematic trends near strong slopes in the raw spectra due to telluric absorption bands at 1.4 and 1.8~$\mu$m.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets.}
	\label{fig:tserPfold}
\end{figure*}

2MASS J0835 exhibits very little variability over our 4.8 hr whereas 2MASS 1821 shows large varations when phasing the dynamic spectra at the known rotation periods of the two brown dwarfs, shown in Figure \ref{fig:tserPfold}.
For 2MASS 1821, the variations are mostly sinusoidal and repeat over multiple rotations of the brown dwarf - the exception is wavelengths near telluric features, such as 1.43~$\mu$m and 1.79~$\mu$m.
